\begin{thebibliography}{99}
\bibitem{BarnettAlex} 
Barnett, Alex. So what is this Platformas a Service Thing
\\\texttt{http://alexbarnett.net}

\bibitem{Llorente} 
Llorente, I. M. 
\textit{Towards a new model for the infrastructure grid. Panel FromGrids to Cloud Services in the International Advanced Research Workshop on High Performance Computing and Grids}. Cetraro, Italy, July 2008.
 
\bibitem{Andressen} 
Andressen, Marc. The three kinds of platforms you meet on the Internet
\\\texttt{http://blog.pmarca.com}

\bibitem{MacVittie} 
MacVittie, Lori. As a Service: The many faces of the cloud
\\\texttt{http://devcentral.f5.com/weblogs/macvittie/Default.aspx}

\bibitem{Macvitti} 
MacVittie, Lori. Bursting the Cloud
\\\texttt{http://devcentral.f5.com/weblogs/macvittie/archive/2008/09/03/}

\bibitem{Webopedia} 
Webopedia Computer Dictionary. data center tiers 
\\\texttt{http://www.webopedia.com/TERM/D/data\_center\_tiers.html}

\bibitem{Andreessen} 
Andreessen, Marc. Analyzing the Facebook Platform
\\\texttt{http://blog.pmarca.com/2007/06/analyzing\_the\_f.html}

\bibitem{Meredith} 
Farkas, Meredith. What is Social Software?
\\\texttt{http://www.sociallibraries.com/farkaschap1.pdf}

\bibitem{Takase} 
Takase, Akihiko D. Sc. And Kikuchi, Susumu. Platform Architecture for Networked Businesses
\\\texttt{http://hitachi.com/ICSFiles/afieldfile/2004/06/01/r2000\_04\_101.pdf} 
 
\bibitem{Webopedia} 
Webopedia Computer Dictionary. data center tiers
\\\texttt{http://www.webopedia.com/TERM/D/data\_center\_tiers.html}

\bibitem{Andrei} 
Andrei Hagiu and David B. Yoffie. Business Harvard Review 
\\\texttt{http://www.hbr.org}

\bibitem{Webopedia} 
Jerry Shenk. Log Management in the Cloud
\\\texttt{http://www.sans.org/}
\end{thebibliography}